\subsection{Technical Issues}

The project required that members familiarise themselves with new forms of technology, for example Django (a python web framework). It was also necessary to regain familiarity with scripting and web-styling languages such as JavaScript and CSS. Inevitably, most of the time invested was spent resolving conflicts, a natural part of the learning process. Web tutorials and books were the main sources of learning.

Members were encouraged to reuse tested pieces of software whenever possible, in accordance with our design principles. This ensured that we minimised the incidence of errors in our code. However, it was still necessary for members to understand the underlying structure of the code which was reused.

For example, integrating multiple JavaScript applications in the web page resulted in issues such as dealing with Mootools library conflicts, multiple library conflicts, "On-load" function conflicts, to name a few. It was necessary for designers to truly understand the workings of the code.

Additionally, there were some Django issues which arose, like improving the search effeciency for recipes. Even setting up a dedicated web server was a convoluted task, where members had to deal with bureaucracy and university red-tape.

Regardless, the team solved such issues with great panache, requiring minimal guidance and relying on each others support to collectively prvail as a team.

\subsection{Time Management Issues}

Beneath the disciplined facade suggested by the groups milestone charts, it was, admittedly, a herculean task negotiating the different deadlines. The main obstacle involved dealing with a variety of university assignments which were doled out on members in an unpredictable manner. However, the solution presented itself in due course- instead of tweaking the milestone chart, some members carried a heavier burden of the project when another members coursework was due, after which these roles were exchanged, to allow the first member time to complete his assignment. It was serendipituous that our members had enrolled in different modules which made this an effective solution.

\subsection{Group Working Issues}

The team has a clear management structure which has prevented any issues. Moreover, this enables members to take responsibility of their areas, thereby ensuring accountability and alleviating conflicts. This also ensures an equitable distribution of workload.

\subsection{Success of Project}

